Video-Agnostic Perturbations: Efficient Targeted Attacks \\ for Siamese Visual Tracking

### 2021-01-18 博士/论文提交/adversarial_attack/IJCAI/FormattingGuidelines-IJCAI-21/main.tex
修改单复数错误

We need to set a specific trajectories $B^{fake}=\{b^{fake}_i\}_1^{T}$ for each video in the dataset to achieve targeted attack, which we call the \textit{fake trajectory}. We call the bounding box ground truth $B^{gt}=\{b^{gt}_i\}_1^T$ the \textit{real trajectory}.
Manually labelling $B^{fake}$ for each video will be time-consuming, so we generate $B^{fake}$ based on $B^{gt}$.
Specifically, the fake trajectory follows the real trajectory and the boundary between $b^{fake}_i$ and $b^{gt}_i$ is 16 pixels apart.
%The size of $b^{fake}_0$ is the same as $B^{gt}_0$ and the size of $b^{fake}_i$
The bounding box size of the fake trajectory gradually changes from the size of $b^{gt}_1$ to $64\times 64$.

>>>>

We need to set a specific trajectory $B^{fake}=\{b^{fake}_i\}_1^{T}$ for each video in the dataset to achieve targeted attack, which we call the \textit{fake trajectory}. We call the bounding box ground truth $B^{gt}=\{b^{gt}_i\}_1^T$ the \textit{real trajectory}.
Manually labelling $B^{fake}$ for each video will be time-consuming, so we generate $B^{fake}$ based on $B^{gt}$.
Specifically, the fake trajectory follows the real trajectory and the boundary between $b^{fake}_i$ and $b^{gt}_i$ is 16 pixels apart.
%The size of $b^{fake}_0$ is the same as $B^{gt}_0$ and the size of $b^{fake}_i$
The bounding box size of the fake trajectory gradually changes from the size of $b^{gt}_1$ to $64\times 64$.
